---
title: "exemple data"
output: html_document
---

usefull comands for python

repl_python()
import random

random.seed(212)
features, target = make_blobs(n_samples = 50, n_features = 5, centers = 4, cluster_std = 0.65, shuffle = True)



#Functions used

```{r}
#function: remove zero varience data
Return.Zero.Variance.Rows = function(mat){
  rowVars <- apply(mat, 1, var);
  isConstant <-(rowVars <= 0.01);
  return(isConstant);
}
 
#function: Keep columns as specified in colList (logicals). 
Keep.Rows = function(mat, rowList) { 
	return(mat[rowList,]); 
}

#keep common patients

keep.common <- function(data){
  common.patient <- intersect(colnames(data[[1]]), colnames(data[[2]]))
  common.patient <- intersect(common.patient, colnames(data[[3]]))
  data[[1]] <- data[[1]][,common.patient]
  data[[2]] <- data[[2]][,common.patient]
  data[[3]] <- data[[3]][,common.patient]
  return(data)
}


#function that remove rows that have variance < than "variance" variable
#arguments: data - list of matrix
#           variance - variance threshold

remove.Zero.varience <- function(data, variance){
  
  #remove zero varience data
  Return.Zero.Variance.Rows = function(mat, variance){
    rowVars <- apply(mat, 1, var);
    isConstant <-(rowVars <= variance);
    return(isConstant);
  }
  #Keep columns as specified in colList (logicals). 
  Keep.Rows = function(mat, rowList) { 
  	return(mat[rowList,]); 
  }
  
  for (view in 1:length(data)){
    view
    zerorowlist <- Return.Zero.Variance.Rows(data[[view]], variance);
    data[[view]]<-Keep.Rows(data[[view]], !zerorowlist);
  }
  return(data)
}



makeSimData <- function (n_views = 3, n_features = 100, n_samples = 50, n_factors = 5, 
    likelihood = "gaussian", DZ = NULL)
{
    if (!all(likelihood %in% c("gaussian", "bernoulli", "poisson"))) 
        stop("Liklihood not implemented: Use either gaussian, bernoulli or poisson")
    if (length(likelihood) == 1) 
        likelihood <- rep(likelihood, n_views)
    if (!length(likelihood) == n_views) 
        stop("Likelihood needs to be a single string or matching the number of views!")
    #latent factors
    
    if(length(DZ)==0){
      Z <- matrix(rnorm(n_factors * n_samples, 0, 1), nrow = n_samples, ncol = n_factors)
    }else{
      Z <- DZ
    }
    
    
    theta <- 0.5
    alpha <- sapply(1:n_factors, function(fc) {
        active_vw <- sample(1:n_views, 1)
        alpha_fc <- sample(c(1, 1000), n_views, replace = TRUE)
        if (all(alpha_fc == 1000)) 
            alpha_fc[active_vw] <- 1
        alpha_fc
    })
    alpha <- t(alpha)
    
    #S- lista matrix de 1 e 0
    S <- lapply(1:n_views, function(vw) matrix(rbinom(n_features * 
        n_factors, 1, theta), nrow = n_features, ncol = n_factors))
    
    #list of matrix W with normal distribuition, mean=0, and sd = 1/alpha
    W <- lapply(1:n_views, function(vw) sapply(1:n_factors, function(fc) rnorm(n_features, 
        0, sqrt(1/alpha[fc, vw]))))
    tau <- 10
    
    
    mu <- lapply(1:n_views, function(vw) Z %*% t(S[[vw]] * W[[vw]]))
    
    
    data <- lapply(1:n_views, function(vw) {
        lk <- likelihood[vw]
        if (lk == "gaussian") {
            dd <- t(mu[[vw]] + rnorm(length(mu[[vw]]), 0, sqrt(1/tau)))
        }
        else if (lk == "poisson") {
            term <- log(1 + exp(mu[[vw]]))
            dd <- t(apply(term, 2, function(tt) rpois(length(tt), 
                tt)))
        }
        else if (lk == "bernoulli") {
            term <- 1/(1 + exp(-mu[[vw]]))
            dd <- t(apply(term, 2, function(tt) rbinom(length(tt), 
                1, tt)))
        }
        colnames(dd) <- paste0("sample_", 1:ncol(dd))
        rownames(dd) <- paste0("feature", 1:nrow(dd))
        dd
    })
    names(data) <- paste0("view_", 1:n_views)
    return(data)
}


```




python for make cluster data
```{r}

library(reticulate)
sklearn <- import("sklearn.datasets")  
py_available(TRUE)
knitr::knit_engines$set(python = reticulate::eng_python)

```


Z:
number_of_test = 8
samples_size = [100]
latents_size = [3,5,10,15]
cluster_size = [2,3,4,5,6,7,8,9]
cluster_std = [0.25,0.5,0.75,1,1.25,1.5,1.75,2]



Y:

```{r}

samples.size <- c(100)
features.size <- c(20,50,100,500,1000)
latents.size <- c(3,5,10,15)
cluster.size <- c(2,3,4,5,6,7,8,9)
views.size <- c(3)




```



repl_python()
```{python}


from sklearn.datasets import make_blobs
from sklearn.cluster import KMeans
import random
import math
import numpy as np

random.seed(212)
# Make features and targets with 500 samples,

samples_size = [100]
latents_size = [3,5,10,15]
cluster_size = [2,3,4,5,6,7,8,9]
cluster_std = [0.25,0.5,0.75,1,1.25,1.5,1.75,2]

samples_index = np.full((len(samples_size),len(latents_size),len(cluster_size),len(cluster_std)), 0)
index = 0
for i in range(0, len(samples_size)):
  for j in range(0, len(latents_size)):
    for k in range(0, len(cluster_size)):
      for l in range(0, len(cluster_std)):
        samples_index[i,j,k,l] = index
        index = index + 1

test_samples = list()
test_labels = list()
for i in range(0, len(samples_size)):
  for j in range(0, len(latents_size)):
    for k in range(0, len(cluster_size)):
      for l in range(0, len(cluster_std)):
        data, label = make_blobs(n_samples = samples_size[i], n_features = latents_size[j], centers = cluster_size[k], cluster_std = cluster_std[l], shuffle = True,   random_state=0)
        test_samples.append(data)
        test_labels.append(label)




```


get python variables
```{r}
library(MOFA)
library(clusterCrit)
library(factoextra)
library(NbClust)


latent <- py$test_samples
labels <- py$test_labels
Z.index <- py$samples_index

#normalization of list of Zt
for (l in 1:length(latent)){
  latent[[l]]<- scale(latent[[l]])
}

#data transformation from Z to Y
set.seed(1234)


samples.size <- c(100)
features.size <- c(20,50,100,500,1000)
latents.size <- c(3,5,10,15)
cluster.size <- c(2,3,4,5,6,7,8,9)
views.size <- c(3)
cluster.std <- c(0.25,0.5,0.75,1,1.25,1.5,1.75,2)

Y.index <- array(0, dim=c(length(samples.size),length(latents.size),length(cluster.size),length(cluster.std),length(views.size),length(features.size)))
Y.samples <- list()
Y.labels <- list()

index <- 1
for(i in 1:length(samples.size)){
  for(j in 1:length(latents.size)){
    for(k in 1:length(cluster.size)){
      for(l in 1:length(cluster.std)){
        for(m in 1:1){            #length(views.size)
          for(n in 1:length(features.size)){      #length(features.size)
            if(features.size[[n]] > latents.size[[j]]){
              print(index)
              Y.samples[[index]] <- makeSimData(n_views = 3, n_features = features.size[[n]], n_samples = samples.size[[i]], n_factors = latents.size[[j]], likelihood = "gaussian", DZ = latent[[Z.index[i,j,k,l]+1]])
              Y.index[i,j,k,l,m,n] <- index
              Y.labels[[index]] <- labels[[Z.index[i,j,k,l]+1]]
              index <- index + 1 
              
            }
          }
        }
      }
    }
  }
}


```




```{r message=FALSE, include=FALSE, results='hide'}

save.image("D:/dissertacao/10_19.RData")

```

rm(latent, labels)


```{r message=FALSE, include=FALSE, results='hide'}
library(MOFA)

Mofa.cluster.index <- vector("list", length = length(Y.samples))
Mofa.real.index <- vector("list", length = length(Y.samples))
mofa.result <- vector("list", length = length(Y.samples))


index <- 1
for(i in 1:1){       #length(samples.size)
  for(j in 1:length(latents.size)){       #length(latents.size)
    for(k in 1:length(cluster.size)){
      for(l in 1:length(cluster.std)){
        for(m in 1:1){            #length(views.size)
          for(n in 1:length(features.size)){      #length(features.size)
            if(features.size[[n]] > latents.size[[j]]){
              if(index > 1019){
  
  data <- Y.samples[[Y.index[i,j,k,l,m,n]]]
  MOFAobject <- createMOFAobject(data)
  MOFAobject
  plotDataOverview(MOFAobject)
  
  TrainOptions <- getDefaultTrainOptions()
  if(n > 4){
    TrainOptions$tolerance <- 0.2
  }
  TrainOptions
  ModelOptions <- getDefaultModelOptions(MOFAobject)
  ModelOptions$numFactors <- 15
  #ModelOptions$likelihood <- "gaussian"
  DataOptions <- getDefaultDataOptions()
  DataOptions
  TrainOptions$DropFactorThreshold <- 0.03
  
  n_inits <- 5
  MOFAlist <- lapply(seq_len(n_inits), function(it) {
    TrainOptions$seed <- 2018+ it
    MOFAobject <- prepareMOFA(MOFAobject, DataOptions = DataOptions, ModelOptions = ModelOptions, TrainOptions = TrainOptions)
    runMOFA(MOFAobject)
  })

  compareModels(MOFAlist)
  compareFactors(MOFAlist)
  
  MOFAobject <- selectModel(MOFAlist, plotit = FALSE)
  save(MOFAobject, file = paste0("D:/dissertacao/resultado1/",Y.index[i,j,k,l,m,n], "_",i,j,k,l,m,n,".Rdata"))
        
              }
              index <- index + 1 
              print(index)
  
       }
          }
        }
      }
    }
  }
}



save.image("D:/dissertacao/10_21_1.RData")


```



```{r}
library("clusterCrit")
library("NbClust")
library("cluster")
library("factoextra")

Mofa.cluster.index.sihouette <- vector("list", length = length(Y.samples))
Mofa.real.index <- vector("list", length = length(Y.samples))
mofa.result <- vector("list", length = length(Y.samples))
Mofa.cluster.index.wss <- vector("list", length = length(Y.samples))

Mofa.lf.found <- list()
Mofa.k.found.sil <- list()
Mofa.k.found.wss <- list()


index <- 1
for(i in 1:1){       #length(samples.size)
  for(j in 1:length(latents.size)){       #length(latents.size)
    for(k in 1:length(cluster.size)){
      for(l in 1:length(cluster.std)){
        for(m in 1:1){            #length(views.size)
          for(n in 1:length(features.size)){      #length(features.size)
            if(features.size[[n]] > latents.size[[j]]){
              if(index > 0){
                load(paste0("D:/dissertacao/resultado1/",Y.index[i,j,k,l,m,n], "_",i,j,k,l,m,n,".Rdata"))
  latentZmofa <- MOFAobject@Expectations[["Z"]]
  Mofa.lf.found[[Y.index[i,j,k,l,m,n]]] <- dim(latentZmofa)[2]
  clusterRef <- as.integer(Y.labels[[Y.index[i,j,k,l,m,n]]]+1)
  
  #by silhouette
  cluster.index <- NbClust(data = latentZmofa, distance = "euclidean", min.nc = 2, max.nc = 10, method = "kmeans", index= "silhouette")
  Mofa.cluster.index.sihouette[[Y.index[i,j,k,l,m,n]]] <- extCriteria(cluster.index[["Best.partition"]], clusterRef, "all")
  Mofa.k.found.sil[[Y.index[i,j,k,l,m,n]]] <- cluster.index$Best.nc[[1]]
  
  #by real clusters
  clusterMofa <- kmeans(latentZmofa, cluster.size[[k]], nstart = 25)
  Mofa.real.index[[Y.index[i,j,k,l,m,n]]] <- extCriteria(clusterMofa$cluster, clusterRef, "all")
  
  #by wss
  nbcluster <- fviz_nbclust(x = latentZmofa,FUNcluster = kmeans, method = 'wss' )
  n.cluster <- find.k.by.second.derivative(nbcluster$data$y)
  clusterMofa.wss <- kmeans(latentZmofa, n.cluster, nstart = 25)
  Mofa.cluster.index.wss[[Y.index[i,j,k,l,m,n]]] <- extCriteria(clusterMofa.wss$cluster, clusterRef, "all")
  Mofa.k.found.wss[[Y.index[i,j,k,l,m,n]]] <- n.cluster
  
              }
              print(index)
  
  index <- index + 1
  
  
       }
          }
        }
      }
    }
  }
}


```




i  samples.size <- c(50,100,500)
m  features.size <- c(20,50,100,500,1000)
j  latents.size <- c(2,5,10,15)
k  cluster.size <- c(2,3,4,5,6,7,8,9)
n  views.size <- c(3)
l  cluster.std <- c(0.25,0.5,0.75,1,1.25,1.5,1.75,2)



```{r}

for(a in 1:length(cluster.std)){
  if(features.size[[n]] > latents.size[[j]]){
    
  real.index <- Mofa.real.index[[Y.index[i,j,k,a,m,n]]]
  wss <- Mofa.cluster.index.wss[[Y.index[i,j,k,a,m,n]]]
  silhouette <- Mofa.cluster.index.sihouette[[Y.index[i,j,k,a,m,n]]]
  
  cluster.index[a,1] <- real.index$precision
  cluster.index[a,2] <- real.index$recall
  cluster.index[a,3] <- real.index$jaccard
  cluster.index[a,4] <- real.index$rand
  cluster.index[a,5] <- real.index$folkes_mallows
  
  silhouette.index[a,1] <- silhouette$precision
  silhouette.index[a,2] <- silhouette$recall
  silhouette.index[a,3] <- silhouette$jaccard
  silhouette.index[a,4] <- silhouette$rand
  silhouette.index[a,5] <- silhouette$folkes_mallows
  
  wss.index[a,1] <- wss$precision
  wss.index[a,2] <- wss$recall
  wss.index[a,3] <- wss$jaccard
  wss.index[a,4] <- wss$rand
  wss.index[a,5] <- wss$folkes_mallows


  }
}
```


```{r}


index <- 1

i <- 1      #samples.size <- c(100)
j <- 1      #latents.size <- c(2,5,10,15)
k <- 4      #cluster.size <- c(2,3,4,5,6,7,8,9)
l <- 1      #cluster.std <- c(0.25,0.5,0.75,1,1.25,1.5,1.75,2)
m <- 1      #views.size <- c(3)
n <- 1      #features.size <- c(20,50,100,500,1000)

cluster.index <- matrix(0L, nrow = length(cluster.std), ncol = 5)
silhouette.index <- matrix(0L, nrow = length(cluster.std), ncol = 5)
wss.index <- matrix(0L, nrow = length(cluster.std), ncol = 5)

colnames(cluster.index) <- c("precision","recall","jaccard","rand","folkes_mallows")
rownames(cluster.index) <- paste0("std=", cluster.std[1:length(cluster.std)])

for(j in 1:length(latents.size)){
  for(n in 1:length(features.size)){
    for(k in 1:length(cluster.size)){
      for(a in 1:length(cluster.std)){
        real.index <- Mofa.real.index[[Y.index[i,j,k,a,m,n]]]
        wss <- Mofa.cluster.index.wss[[Y.index[i,j,k,a,m,n]]]
        silhouette <- Mofa.cluster.index.sihouette[[Y.index[i,j,k,a,m,n]]]
        
          cluster.index[a,1] <- cluster.index[a,1] + real.index$precision
          cluster.index[a,2] <- cluster.index[a,2] + real.index$recall
          cluster.index[a,3] <- cluster.index[a,3] + real.index$jaccard
          cluster.index[a,4] <- cluster.index[a,4] + real.index$rand
          cluster.index[a,5] <- cluster.index[a,5] + real.index$folkes_mallows
          
          silhouette.index[a,1] <- silhouette.index[a,1] + silhouette$precision
          silhouette.index[a,2] <- silhouette.index[a,2] + silhouette$recall
          silhouette.index[a,3] <- silhouette.index[a,3] + silhouette$jaccard
          silhouette.index[a,4] <- silhouette.index[a,4] + silhouette$rand
          silhouette.index[a,5] <- silhouette.index[a,5] + silhouette$folkes_mallows
          
          wss.index[a,1] <- wss.index[a,1] + wss$precision
          wss.index[a,2] <- wss.index[a,2] + wss$recall
          wss.index[a,3] <- wss.index[a,3] + wss$jaccard
          wss.index[a,4] <- wss.index[a,4] + wss$rand
          wss.index[a,5] <- wss.index[a,5] + wss$folkes_mallows
      }
    }
  }
}




print.cluster.index.fig(cluster.index/(4*5*8))
print.cluster.index.fig(silhouette.index/(4*5*8))
print.cluster.index.fig(wss.index/(4*5*8))




```



```{r}

features.lf <- list()


for(j in 1:length(latents.size)){
  features.lf[[j]] <- list()
  for(n in 1:length(features.size)){
    features.lf[[j]][[n]] <-list()
    for(k in 1:length(cluster.size)){
      for(l in 1:length(cluster.std)){
        features.lf[[j]][[n]] <- c(features.lf[[j]][[n]], Mofa.lf.found[[Y.index[1,j,k,l,1,n]]])
        
      }
    }
  }
}

for(k in 1:length(cluster.size)){
  for(n in 1:length(features.size)){
    vec <- unlist(features.lf[[j]][[n]])
    #geom_bar(vec)
    print(table(vec))
    print("----------------")
}}

```



  
```{r}
k.vs.lf <- list()


for(k in 1:length(cluster.size)){
  k.vs.lf[[k]] <- list()
  for(j in 1:length(latents.size)){
    k.vs.lf[[k]][[j]] <-list()
    for(n in 1:length(features.size)){
      for(l in 1:length(cluster.std)){

        k.vs.lf[[k]][[j]] <- c(k.vs.lf[[k]][[j]], Mofa.k.found.sil[[Y.index[1,j,k,l,1,n]]])
        
      }
    }
  }
}


for(k in 1:length(cluster.size)){
  for(j in 1:length(latents.size)){
    print(paste("Number of cluster:",cluster.size[[k]], "Number of latents : ", latents.size[[j]]))
    vec <- unlist(k.vs.lf[[k]][[j]])
    #geom_bar(vec)
    print(table(vec))
    
}}
```







```{r}

elbow.values <- c(1.00, 0.53, 0.31, 0.28, 0.26, 0.24, 0.21, 0.20, 0.19, 0.16, 0.16)



find.k.by.second.derivative <- function(elbow.values){
  number.of.k <- length(elbow.values)
  first.derivative <- vector()
  for(i in 2:number.of.k - 1){
    first.derivative[[i+1]] <- elbow.values[[i]] - elbow.values[[i+1]]
  }
  second.derivative <- vector()
  for(i in 3:number.of.k-2){
    second.derivative[[i+2]] <- first.derivative[[i+1]] - first.derivative[[i+2]]
  }
  strength <- vector()
  relative.strength <- vector()
  
  
  dist_to_line <- vector()
  for(i in 1:number.of.k){
    dist_to_line[[i]] <- dist2d(c(i,elbow.values[[i]]), c(1,elbow.values[[1]]), c(10,elbow.values[[10]]))
  }
  
  
  check <- 0
  for(i in 3:number.of.k-1){
    if(second.derivative[[i+1]] > first.derivative[[i+1]]){
      strength[[i]] <- second.derivative[[i+1]] - first.derivative[[i+1]]
      relative.strength[[i]] <- strength[[i]]/(i)
      check <- 1
    }
  }
  
  if(check == 0){
    index <- which.max(dist_to_line)
  }else{
    index <- which.max(relative.strength)
  }
  
  
  return(index)
}


print.cluster.index.fig <- function(cluster.index){
  plot(cluster.std, cluster.index[,1],  type="o",  col="blue",  lty=1, ylim=c(0,1), ylab="Index Value" )
  points(cluster.std, cluster.index[,2], col="red")
  lines(cluster.std, cluster.index[,2], col="red",lty=2)
  points(cluster.std, cluster.index[,3], col="green")
  lines(cluster.std, cluster.index[,3], col="green",lty=3)
  points(cluster.std, cluster.index[,4], col="yellow")
  lines(cluster.std, cluster.index[,4], col="yellow",lty=4)
  points(cluster.std, cluster.index[,5], col="gray")
  lines(cluster.std, cluster.index[,5], col="gray",lty=5)
  legend(0.3,0.5,legend=c("precision","recall","jaccard","rand","folkes_mallows"), col=c("blue","red","green","yellow","gray"), lty=c(1,2,3,4,5), ncol=1)
}


dist2d <- function(a,b,c) {
 v1 <- b - c
 v2 <- a - b
 m1 <- cbind(v1,v2)
 d <- abs(det(m1))/sqrt(sum(v1*v1))
} 

```




new.samples <- Y.samples[1:1232]
save(new.samples, Y.labels, file = "D:/dissertacao/10_17_Y1.RData")


```{r}

for (i in 1:number.of.test){
  print("--------------------------------")
  print(paste0("precision: ", Mofa.cluster.index[[i]]$precision))
  print(paste0("recall: ", Mofa.cluster.index[[i]]$recall))
  print(paste0("jaccard: ", Mofa.cluster.index[[i]]$jaccard))
  print(paste0("rand: ", Mofa.cluster.index[[i]]$rand))
  print(paste0("folkes_mallows: ", Mofa.cluster.index[[i]]$folkes_mallows))
}

for (i in 1:number.of.test){
  Mofa.real.index[[i]]$precision
  Mofa.real.index[[i]]$recall
  Mofa.real.index[[i]]$jaccard
  Mofa.real.index[[i]]$rand
  Mofa.real.index[[i]]$folkes_mallows
}

```





repl_python()
```{python}

from sklearn.datasets import make_blobs
from sklearn.cluster import KMeans
import random
import math

def Cluster_print(cluster):
  n_cluster = len(cluster)
  for i in range(n_cluster):
    print("Cluster number:", i+1, " contains", len(cluster[i]), "elements.")

random.seed(212)
# Make features and targets with 500 samples,
latent = list()
label = list()
features, target = make_blobs(n_samples = 50, n_features = 2, centers = 4, cluster_std = 1, shuffle = True, random_state=0)
latent.append(features)
label.append(target)
features, target = make_blobs(n_samples = 50, n_features = 5, centers = 4, cluster_std = 0.65, shuffle = True, random_state=0)
latent.append(features)
label.append(target)
features, target = make_blobs(n_samples = 100, n_features = 15, centers = 5, cluster_std = 0.65, shuffle = True, random_state=0)
latent.append(features)
label.append(target)

clusters = 4
kmeans = KMeans(n_clusters=clusters, random_state=None).fit(features)
result_label = kmeans.labels_

#C is a list of vectors, that each vector contains the index of each cluster element
C = list()
for i in range(clusters):
  C_i = []
  for j in range(result_label.shape[0]):
    if(result_label[j] == (i+1)):
      C_i.append(j)
  
  C.append(C_i)

Cluster_print(C)

```


get python variables
```{r}
latent <- py$latent
labels <- py$label

```



```{r}
#normalization of list of Z
simdata <- py$latent
for (l in 1:length(simdata)){
  simdata[[l]]<- scale(simdata[[l]])
}


#bin <- cbind(simdata[[1]][,4],simdata[[1]][,2])
#plot(bin, xlab = "Latent factor 4", ylab = "Latent factor 2")


for (l in 1:dim(simdata[[1]])[2]){
  den <- density(simdata[[1]][,l])
  plotname <- paste("Distribuition of feature ", l) 
  plot(main = plotname, den)
}

```


kmeans
```{r}
library(cluster)
library(fpc)

k.result <- kmeans(simdata[[1]], 4, nstart = 10)
plotcluster(simdata[[1]], k.result$cluster, xlab = "Latent factor 1", ylab = "Latent factor 2")



```


make simulated data function


n_views = 3
n_features = 100 
n_samples = 50 
n_factors = 5
likelihood = "gaussian"


```{r}


makeSimData <- function (n_views = 3, n_features = 100, n_samples = 50, n_factors = 5, 
    likelihood = "gaussian", DZ = NULL)
{
    if (!all(likelihood %in% c("gaussian", "bernoulli", "poisson"))) 
        stop("Liklihood not implemented: Use either gaussian, bernoulli or poisson")
    if (length(likelihood) == 1) 
        likelihood <- rep(likelihood, n_views)
    if (!length(likelihood) == n_views) 
        stop("Likelihood needs to be a single string or matching the number of views!")
    #latent factors
    
    if(length(DZ)==0){
      Z <- matrix(rnorm(n_factors * n_samples, 0, 1), nrow = n_samples, ncol = n_factors)
    }else{
      Z <- DZ
    }
    
    
    theta <- 0.5
    alpha <- sapply(1:n_factors, function(fc) {
        active_vw <- sample(1:n_views, 1)
        alpha_fc <- sample(c(1, 1000), n_views, replace = TRUE)
        if (all(alpha_fc == 1000)) 
            alpha_fc[active_vw] <- 1
        alpha_fc
    })
    alpha <- t(alpha)
    
    #S- lista matrix de 1 e 0
    S <- lapply(1:n_views, function(vw) matrix(rbinom(n_features * 
        n_factors, 1, theta), nrow = n_features, ncol = n_factors))
    
    #list of matrix W with normal distribuition, mean=0, and sd = 1/alpha
    W <- lapply(1:n_views, function(vw) sapply(1:n_factors, function(fc) rnorm(n_features, 
        0, sqrt(1/alpha[fc, vw]))))
    tau <- 10
    
    
    mu <- lapply(1:n_views, function(vw) Z %*% t(S[[vw]] * W[[vw]]))
    
    
    data <- lapply(1:n_views, function(vw) {
        lk <- likelihood[vw]
        if (lk == "gaussian") {
            dd <- t(mu[[vw]] + rnorm(length(mu[[vw]]), 0, sqrt(1/tau)))
        }
        else if (lk == "poisson") {
            term <- log(1 + exp(mu[[vw]]))
            dd <- t(apply(term, 2, function(tt) rpois(length(tt), 
                tt)))
        }
        else if (lk == "bernoulli") {
            term <- 1/(1 + exp(-mu[[vw]]))
            dd <- t(apply(term, 2, function(tt) rbinom(length(tt), 
                1, tt)))
        }
        colnames(dd) <- paste0("sample_", 1:ncol(dd))
        rownames(dd) <- paste0("feature", 1:nrow(dd))
        dd
    })
    names(data) <- paste0("view_", 1:n_views)
    return(data)
}


```



Data transformation, Z to Y
```{r}

set.seed(1234)
simulated.data <- list()
simulated.data[[1]] <- makeSimData(n_views = 3, n_features = 20, n_samples = 50, n_factors = 2, likelihood = "gaussian", DZ = simdata[[1]])
simulated.data[[2]] <- makeSimData(n_views = 3, n_features = 100, n_samples = 50, n_factors = 5, likelihood = c("gaussian", "poisson", "bernoulli"), DZ = simdata[[2]])
simulated.data[[3]] <- makeSimData(n_views = 3, n_features = 200, n_samples = 100, n_factors = 15, likelihood = "gaussian", DZ = simdata[[3]])




```




```{r}
#library(MOFAtools)
library(MOFA)

#filtra variaveis com varianca inferior a 1%
processed.data <- list()
for (l in 1:length(simulated.data)){
  processed.data[[l]] <- remove.Zero.varience(simulated.data[[l]], 0.01)
}


#MOFAobject <- createMOFAobject(simulated.data[[1]])

MOFAobject <- createMOFAobject(processed.data[[1]])
MOFAobject

plotDataOverview(MOFAobject)
```



```{r}
for(feature in 1:dim(simulated.data$view_1)[1]){
  print(paste("feature number:", feature))
  den <- density(simulated.data$view_1[feature,])
  plot(den)
}

```



```{r}
TrainOptions <- getDefaultTrainOptions()
TrainOptions
ModelOptions <- getDefaultModelOptions(MOFAobject)
ModelOptions
DataOptions <- getDefaultDataOptions()
DataOptions


TrainOptions$DropFactorThreshold <- 0.01
```











```{r}
n_inits <- 10
MOFAlist <- lapply(seq_len(n_inits), function(it) {
  
  TrainOptions$seed <- 2018
  
  MOFAobject <- prepareMOFA(
  MOFAobject, 
  DataOptions = DataOptions,
  ModelOptions = ModelOptions,
  TrainOptions = TrainOptions
)
  
  runMOFA(MOFAobject)
})

```




```{r}
compareModels(MOFAlist)
```


```{r}
compareFactors(MOFAlist)
```



```{r}
MOFAobject <- selectModel(MOFAlist, plotit = FALSE)
MOFAobject
```




downstream analysis

```{r}
plotVarianceExplained(MOFAobject)
```

latent variables
```{r}

latentZmofa <- MOFAobject@Expectations[["Z"]]
for(feature in 1:dim(latentZmofa)[2]){
  print(paste("feature number:", feature))
  den <- density(latentZmofa[,feature])
  plot(den)
}

```




```{r}
library("clusterCrit")
clusterMofa <- kmeans(latentZmofa, 4, nstart = 25)
clusterMofa$cluster
clusterRef <- as.integer(py$target)


clusterCrteria <- extCriteria(clusterMofa$cluster, clusterRef, "all")
clusterCrteria$precision
clusterCrteria$recall
clusterCrteria$jaccard
clusterCrteria$rand
clusterCrteria$folkes_mallows

```




```{r}
k.result <- kmeans(simdata[[1]], 4, nstart = 10)
plotcluster(simdata[[1]], k.result$cluster, xlab = "Latent factor 1", ylab = "Latent factor 2")

plotcluster(latentZmofa, clusterMofa$cluster, xlab = "Latent factor 1", ylab = "Latent factor 2")


```




#é necessario correr com repl_python() para versoes de rstudio < 1.24

```{python}


```




iClusterPlus

Note:
-the matrix used for functions are suposed to be samples on row and features on coluns, different from MOFA




```{r}
library(iClusterPlus)
library(GenomicRanges)
library(gplots)
library(lattice)

```



```{r}




for(k in 1:8){
  cv.fit = tune.iClusterPlus(cpus=1,dt1=t(processed.data[[1]]$view_1),dt2=t(processed.data[[1]]$view_2),dt3=t(processed.data[[1]]$view_3),
  type=c("gaussian","gaussian","gaussian"),K=k,n.lambda=185,
  scale.lambda=c(1,1,1),maxiter=20)
  save(cv.fit, file=paste("cv.fit.k",k,".Rdata",sep=""))
}


```







```{r}

output=alist()

files=grep("cv.fit",dir())

for(i in 1:length(files)){
  load(dir()[files[i]])
  output[[i]]=cv.fit
  
}

nLambda = nrow(output[[1]]$lambda)
nK = length(output)

BIC = getBIC(output)
devR = getDevR(output)



```




```{r}

minBICid = apply(BIC,2,which.min)

devRatMinBIC = rep(NA,nK)

for(i in 1:nK){
  devRatMinBIC[i] = devR[minBICid[i],i]
}




```


```{r}

plot(1:(nK+1),c(0,devRatMinBIC),type="b",xlab="Number of clusters (K+1)", ylab="%Explained Variation")

```



```{r}

clusters=getClusters(output)
rownames(clusters)=rownames(t(simulated.data$view_1))
colnames(clusters)=paste("K=",2:(length(output)+1),sep="")




#write.table(clusters, file="clusterMembership.txt",sep='\t',quote=F)

k=3
best.cluster=clusters[,k]
best.fit=output[[k]]$fit[[which.min(BIC[,k])]]

clusterCrteria <- extCriteria(best.cluster, clusterRef, "all")
print("Precision:",clusterCrteria$precision)
clusterCrteria$recall
clusterCrteria$jaccard
clusterCrteria$rand
clusterCrteria$folkes_mallows

best.lantent <- best.fit$meanZ
rownames(best.lantent) <- rownames(t(simulated.data$view_1))
for(feature in 1:dim(best.lantent)[2]){
  print(paste("feature number:", feature))
  den <- density(best.lantent[,feature])
  plot(den)
}



```






```{r}
W <- best.fit$beta

for (l in 1:length(W)){
  rownames(W[[l]]) <- rownames(simulated.data$view_1)
  colnames(W[[l]]) <- c("lf1","lf2","lf3","lf4","lf5")
}




#lista com pesos de cada variave em difenrentes view na latent variable (nao funciona quando tem features difenrentes em cada view)
fw <- list()
for (l in 1:dim(W[[1]])[2]){
  fw[[l]] <- matrix(data = 1:dim(W[[1]])[1], nrow = dim(W[[1]])[1], ncol = 1)  
  for (v in 1:length(W)){
    fw[[l]] <- cbind(fw[[l]], W[[v]][,l])
  }
  fw[[l]]<-fw[[l]][,-1]
  rownames(fw[[l]]) <- rownames(simulated.data$view_1)
}


#lista com pesos de cada lf em cada view (cumprimento total=v*f)
fwl <- list()

i <- 0
for (l in 1:dim(W[[1]])[2]){
  for (v in 1:length(W)){
    i <- i + 1 
    fwl[[i]] <- W[[v]][,l]
  }
}


#remove 0 weight features
fwl <- lapply(fwl, function(x) {x[x!=0]})

#sort feature weights
fwl <- lapply(fwl, function(x) {x[order(abs(x), decreasing = TRUE)]})



fwl[[1]][order(abs(fwl[[1]]), decreasing = TRUE)]








W1 <- best.fit$beta[[1]]
heatmap(W1)



```




Cluster result figure

```{r}
library(condformat)


smoke <- matrix(c(51,43,22,92,28,21,68,22,9),ncol=3,byrow=TRUE)
colnames(smoke) <- c("High","Low","Middle")
rownames(smoke) <- c("current","former","never")
smoke <- as.table(smoke)
smoke

```


